---
title: "R Notebook"
output: html_notebook
---

```{r}
library(dplyr)
library(lubridate)
library(zoo)
library(data.table)
library(plyr)
```


Data Sets
```{r}
MAHealth <- rio::import("../../Data/MAHealthRankings.xlsx")
MAT21 <- rio::import("../../Data/MA21Clean.xlsx")
MACounty <- rio::import("../../Data/CountyTownMA.xlsx")
```

Viewing Data Header
```{r}
head(MAHealth) #Junyan's MA Health Rankings
head(MAT21) #T21 established counties
head(MACounty) #County Information in MA
```

Clean Data
```{r}
MAT21 <- MAT21[,c(2:3)]
head(MAT21)
```


Left_Joins
```{r}
MACTown21 <- MACounty %>% left_join(MAT21, by = c("Name" = "Town"))
MACTownHealth21 <- MACTown21 %>% left_join(MAHealth, by = c("County", "County"))
head(MACTownHealth21)
write.csv(MACTownHealth21, "../../Data/MACTownHealth21.csv")
```

Getting the Year of T21
```{r}
MACTownHealth21$T21Date <- as.Date(MACTownHealth21$T21Date)
MACTownHealth21$T21year <- year(MACTownHealth21$T21Date)
attach(MACTownHealth21)
#Data needs to be fixed and cleaned or we need to crawl a more updated site
max(T21year, na.rm = TRUE)
min(T21year, na.rm = TRUE)
names(MACTownHealth21)
```

Expand the data to get into Event History Analysis Form
```{r}
pdata <- with(MACTownHealth21, expand.grid(T21year = seq(min(T21year, na.rm = TRUE), max(T21year, na.rm = TRUE)),id = unique(Name)))
View(pdata)
```

Making the data
```{r}
MACTownHealth21_intm <- MACTownHealth21[,c(1,119)] #Get the Name of the twon to match and get the T21 year.
MACTownHealth21_intm <- pdata %>% left_join(MACTownHealth21_intm, by = c("id" = "Name"))
colnames(MACTownHealth21_intm) <- c("year", "TownName", "Event")
```

Recoding everything to 0s
```{r}
MACTownHealth21_intm[is.na(MACTownHealth21_intm$Event),]$Event <- "0"
```

If the event happens at a particular year, code it 1. Otherwise, 0.
```{r}
MACTownHealth21_intm <- mutate(MACTownHealth21_intm, Event = ifelse(Event == year, "1", "0"))
View(MACTownHealth21_intm)
```

Converting Event to Numeric Variable
```{r}
MACTownHealth21_intm$Event <- as.numeric(MACTownHealth21_intm$Event)
```

CumSum to subset the years Town has T21 to get the distance going
```{r}
MACTownHealth21_intm_3 <- MACTownHealth21_intm %>% group_by(TownName) %>% mutate(Sub = cumsum(Event))
```

All the towns has T21 after the initial policy year
```{r}
MACTownDistance <- MACTownHealth21_intm_3[MACTownHealth21_intm_3$Sub ==1,]
View(MACTownDistance)
```

Ordering all by years
```{r}
MACTownDistance_2 <- MACTownDistance[order(MACTownDistance$year),]
View(MACTownDistance_2)
```

```{r}
write.csv(MACTownDistance_2,"../../Data/matowndistyear.csv")
```


<!-- Get the Number of Rows by Each Group for Matrix -->
<!-- ```{r} -->
<!-- MACTownMax <- MACTownDistance %>% group_by(year) %>% tally() -->
<!-- colnum <- max(MACTownMax$n) -->
<!-- rownum <- nrow(MACTownMax) -->
<!-- ``` -->

Junyan's data set 










Join this to County Health Data 
```{r}
MACTownHealth21_intm <- MACTownHealth21_intm %>% left_join(MACTownHealth21, by = c("TownName" = "Name"))
View(MACTownHealth21_intm)
```

Sample Merged Data Set Write Out
```{r}
write.csv(MACTownHealth21_intm, "../../Data/FirstAData.csv")
```



```{r}
MACTownHealth21_intm$year
MACTownHealth21_intm$Event
```


