---
title: "R Notebook"
output: html_notebook
---

```{r}
library(dplyr)
library(lubridate)
library(zoo)
library(data.table)
library(plyr)
```


Data Sets
```{r}
MAHealth <- rio::import("../../Data/MAHealthRankings.xlsx")
MAT21 <- rio::import("../../Data/MA21Clean.xlsx")
MACounty <- rio::import("../../Data/CountyTownMA.xlsx")
```

Viewing Data Header
```{r}
head(MAHealth) #Junyan's MA Health Rankings
head(MAT21) #T21 established counties
nrow(MAT21)
head(MACounty) #County Information in MA
```

Clean Data
```{r}
MAT21 <- MAT21[,c(2:3)]
head(MAT21)
```


Left_Joins
```{r}
MACTown21 <- MACounty %>% left_join(MAT21, by = c("Name" = "Town"))
MACTownHealth21 <- MACTown21 %>% left_join(MAHealth, by = c("County", "County"))
write.csv(MACTownHealth21, "../../Data/MACTownHealth21.csv")
```

Getting the Year of T21
```{r}
MACTownHealth21$T21Date <- as.Date(MACTownHealth21$T21Date)
MACTownHealth21$T21year <- year(MACTownHealth21$T21Date)
#attach(MACTownHealth21)
#Data needs to be fixed and cleaned or we need to crawl a more updated site
max(T21year, na.rm = TRUE)
min(T21year, na.rm = TRUE)
names(MACTownHealth21)
#2018 is impossible so, we can fix it here.
MACTownHealth21[!is.na(MACTownHealth21$T21year) & (MACTownHealth21$T21year == 2018),]$T21year <- 2017
max(MACTownHealth21$T21year, na.rm = TRUE)

```

Expand the data to get into Event History Analysis Form
```{r}
pdata <- with(MACTownHealth21, expand.grid(T21year = seq(min(T21year, na.rm = TRUE), max(T21year, na.rm = TRUE)),id = unique(Name)))
View(pdata)
length(unique(pdata$id))
```

Making the data
```{r}
MACTownHealth21_intm <- MACTownHealth21[,c(1,119)] #Get the Name of the twon to match and get the T21 year.
MACTownHealth21_intm <- pdata %>% left_join(MACTownHealth21_intm, by = c("id" = "Name"))
colnames(MACTownHealth21_intm) <- c("year", "TownName", "Event")
```

Recoding everything to 0s
```{r}
MACTownHealth21_intm[is.na(MACTownHealth21_intm$Event),]$Event <- "0"
```

If the event happens at a particular year, code it 1. Otherwise, 0.
```{r}
MACTownHealth21_intm <- mutate(MACTownHealth21_intm, Event = ifelse(Event == year, "1", "0"))
View(MACTownHealth21_intm)
length(unique(MACTownHealth21_intm$TownName))
```

Converting Event to Numeric Variable
```{r}
MACTownHealth21_intm$Event <- as.numeric(MACTownHealth21_intm$Event)
MACTownHealth21_final <- MACTownHealth21_intm[MACTownHealth21_intm$Event ==1,]
#View(MACTownHealth21_final)
nrow(MACTownHealth21_final)
write.csv(MACTownHealth21_final, "../../Data/matownyearfinal.csv")
```

CumSum to subset the years Town has T21 to get the distance going
```{r}
MACTownHealth21_intm_3 <-  MACTownHealth21_intm %>% group_by(TownName) %>% mutate(Sub = cumsum(Event))

```

Something going on with Dplyr code
```{r}
MACTownHealth21_intm_3 <- data.table(MACTownHealth21_intm_3, key = "TownName")
MACTownHealth21_intm_3[, csum := cumsum(Event), by = key(MACTownHealth21_intm_3)]
View(MACTownHealth21_intm_3)
MACTownHealth21_intm_3 <- data.frame(MACTownHealth21_intm_3)
MACTownHealth21_intm_3 <- MACTownHealth21_intm_3[,-4]
```

```{r}
tmp <- read.csv("../../Data/matowndistyear.csv")
View(tmp)
```

```{r}
MACTownHealth21_intm_4 <- MACTownHealth21_intm_3[order(MACTownHealth21_intm_3$year),]
View(MACTownHealth21_intm_4)
MACTownHealth21_intm_4 <- MACTownHealth21_intm_4[!(MACTownHealth21_intm_4$Event == 0 & MACTownHealth21_intm_4$csum == 0),]

```

```{r}
write.csv(MACTownHealth21_intm_4,"../../Data/matowndistyear_edited.csv")
```


<!-- Get the Number of Rows by Each Group for Matrix -->
<!-- ```{r} -->
<!-- MACTownMax <- MACTownDistance %>% group_by(year) %>% tally() -->
<!-- colnum <- max(MACTownMax$n) -->
<!-- rownum <- nrow(MACTownMax) -->
<!-- ``` -->

Junyan's data set 










Join this to County Health Data 
```{r}
MACTownHealth21_intm <- MACTownHealth21_intm %>% left_join(MACTownHealth21, by = c("TownName" = "Name"))
View(MACTownHealth21_intm)
```

Sample Merged Data Set Write Out
```{r}
write.csv(MACTownHealth21_intm, "../../Data/FirstAData.csv")
```



```{r}
MACTownHealth21_intm$year
MACTownHealth21_intm$Event
```



