---
title: "R Notebook"
output: html_notebook
---

Need an updated T21 data set
```{r}
library(ggmap)
library(rio)
```

Helper function to paste MA in

```{r}
pasteMA <- function (x){
  x <- paste(x, "Massachusetts", sep = " , " )
  return (x)
}
```

Load the Boston Cities with T21 and pasting in the State
```{r}
MA21 <- rio::import("../../Data/MA21Clean.xlsx")
MA21_lonlat <- data.frame(MA21[,2])
colnames(MA21_lonlat) <- c("CityTown")
MA21_lonlat$CityTown
MA21_lonlat <- apply(MA21_lonlat,2, pasteMA)
View(MA21_lonlat)
```

Getting Longitudes and Latitudes
```{r}
MA21_lonlat_tmp<- apply(MA21_lonlat,2, geocode)
MA21_lonlat_tmp <- data.frame(MA21_lonlat_tmp)
colnames(MA21_lonlat_tmp) <- c("lon", "lat")
View(MA21_lonlat_tmp)
View(MA21_lonlat)
```

Data Set with Lat Long
```{r}
MA21_lonlat <- cbind(MA21_lonlat, MA21_lonlat_tmp$lon, MA21_lonlat_tmp$lat)
colnames(MA21_lonlat)[c(2,3)] <- c("lon", "lat")
View(MA21_lonlat)
write.csv(MA21_lonlat,"../../Data/MA21_lonlat.csv")
```

Fill the NAs manually
```{r}
#check if there are any NAs and manually fill them
#17 NAs

#Amherst      72.5199, 42.3732
#Andover      71.1368, 42.6583
#Ashland      71.4634, 42.2612
#Brewster     70.0828, 41.7601
#Brimfield    72.2005, 42.1225
#Dedham       71.1677, 42.2436
#Easton       71.1287, 42.0245
#Foxborough   71.2478, 42.0654
#Gloucester   70.6620, 42.6159
#Lee          73.2482, 42.3042
#Methuen      71.1909, 42.7262
#Millis       71.3517, 42.1670
#Needham      71.2378, 42.2809
#North Andover71.1351, 42.6987
#Norwell      70.7928, 42.1615
#Southampon   72.7301, 42.2293
#Wakefield    71.0723, 42.5039
```



Make a map and animate it when you get back

Function to calculate distance and proportion

Output is the ratio of cities  that has T21 in the area.

Review from the reading

50 miles
100 miles

FIPS ACS
