---
title: "R Notebook"
output: html_notebook
---


```{r, warning = FALSE}
library(readxl)
library(data.table)
library(lubridate) #Date Time Object
library(ggplot2)
library(stringr) #Regular expression string splitting
library(rio)
library(MASS)
library(tigris)
library(sp)
library(broom)
library(dplyr)
library(rgdal)
library(rgeos)
library(spdep)
```

Shape Files by Town Boundaries
```{r}
MA_Town_1 <- readOGR("../../Data/towns/TOWNS_POLYM.shp")
MA_Town_2 <- readOGR("../../Data/towns/TOWNS_POLYM.shp")
levels(MA_Town_1$TOWN)[levels(MA_Town_1$TOWN) == "NORTH ATTLEBOROUGH"] <- "north attleboro"
levels(MA_Town_2$TOWN)[levels(MA_Town_2$TOWN) == "NORTH ATTLEBOROUGH"] <- "north attleboro"
```

Algorithm

1) Check if the town is neighbor to another town
2) If it is, check if it has T21 in that year
3) If it has T21, calculate the ratio

```{r}
res <- gTouches(MA_Town_1, MA_Town_2, byid = TRUE)
rownames(res) <- MA_Town_1@data$TOWN
colnames(res) <- MA_Town_1@data$TOWN
View(res)
sum(res)
```

Checking whether Queens or Rooks
```{r}
neighbors <- poly2nb(MA_Town_1, queen = TRUE)
neighbors
```


Getting the list of list from Neighbors object
```{r}
neighbor_list <-lapply(neighbors, unlist)
```

Building empty data frame for neighbor matrix
```{r}
#ncol
ncol <- max(sapply(neighbor_list, length))
nrow <- length(neighbor_list)
neighbormat <- matrix(NA, nrow = nrow, ncol = ncol)
```

Neighbors Matrix with Indexes through a For Loop
```{r}
for(i in 1:nrow(neighbormat)){
  tmp <- unlist(neighbor_list[i])
  len <- length(tmp)
  for(j in 1:len){
    neighbormat[i,j] <- tmp[j]
  }
}
neighbormat <- data.frame(neighbormat)



```

Checking Neighbor list from Polygon matches with Neighbor list from James
```{r}
MAT21_neighbor_year <- read.csv("../../Data/matowndistyear_edited.csv")
MAT21_neighbor_year <- MAT21_neighbor_year[,-1]
MAT21_neighbor_year <- MAT21_neighbor_year[MAT21_neighbor_year$Event == 1 & MAT21_neighbor_year$csum ==1,]
View(MAT21_neighbor_year)
```

```{r}
MA_Town_ids<- data.frame(tolower(MA_Town_1@data$TOWN))
MAT21_neighbor_year$TownName <- as.factor(tolower(MAT21_neighbor_year$TownName))


#leftjoin to get indexes
MA_Town_ids$id <- seq.int(nrow(MA_Town_ids))
names(MA_Town_ids)[1] <-c("TownName") 
MAT21_neighbor_year_index <- MAT21_neighbor_year %>% left_join(MA_Town_ids, by = c("TownName"))
MAT21_neighbor_year_index
```

```{r}
neighbormat_t21 <- neighbormat[MAT21_neighbor_year_index$id,]
neighbormat_t21$index <- row.names(neighbormat_t21)
neighbormat_t21$denom <- apply(neighbormat_t21, 1, function(x) (sum(!is.na(x))))
```

```{r}
yearratio <- function(neighbormat_t21, MAT21_neighbor_year_index, year){

  tmp1 <- neighbormat_t21 #neighbors matrix
  tmp3 <- neighbormat_t21[,c(1:10)]
  tmp2 <- MAT21_neighbor_year_index #all the MAT21 indexes
  
  #grab the year we are interested in
  #browser()
  tmpyear <- tmp2[tmp2$year %in% c(2009:year-1),]
  
  tmpyear <- unique(tmpyear)
  
  #browser()
  tmp1$num <- apply(tmp3, 1, function(x) sum(x %in% tmpyear$id))
  tmp1$ratio <- tmp1$num/tmp1$denom
  #browser()
  tmp1$index <- as.character(tmp1$index)
  tmp2$id <- as.character(tmp2$id)
 
  tmpfinal <- tmp2 %>% left_join(tmp1, by = c("id" = "index"))
  tmpfinal <- tmpfinal[,c("TownName", "ratio")]
  tmpfinal$year <- c(year)
  return(tmpfinal)
}
```


```{r}
neighbor_2010 <- yearratio(neighbormat_t21,MAT21_neighbor_year_index,2010)
neighbor_2011 <- yearratio(neighbormat_t21,MAT21_neighbor_year_index,2011)
neighbor_2012 <- yearratio(neighbormat_t21,MAT21_neighbor_year_index,2012)
neighbor_2013 <- yearratio(neighbormat_t21,MAT21_neighbor_year_index,2013)
neighbor_2014 <- yearratio(neighbormat_t21,MAT21_neighbor_year_index,2014)
neighbor_2015 <- yearratio(neighbormat_t21,MAT21_neighbor_year_index,2015)

neighbor_2016 <- yearratio(neighbormat_t21,MAT21_neighbor_year_index,2016)
neighbor_2017 <- yearratio(neighbormat_t21,MAT21_neighbor_year_index,2017)
```


```{r}
borderratios <- rbind(neighbor_2010, neighbor_2011, neighbor_2012, neighbor_2013, neighbor_2014, neighbor_2015, neighbor_2016, neighbor_2017)
write.csv(borderratios, "../../Data/borderratios.csv")
```


```{r}

tmp1
tmp2[tmp2$TownName == "norwood",]
tmp1[tmp1$index == 236,]
sum(tmp2$id %in% tmp1[tmp1$index == 236,])

```

