---
title: "R Notebook"
output: html_notebook
---
Loading the libraries
```{r, warning=FALSE}
library(dplyr)
library(lme4)
library(lmerTest)
```

Getting the Master File

```{r}
master <- rio::import("../../Data/master.csv")
#View(master)
#names(master)
#Dropping Chlamydia Rate becasue we do NOT understand the measurement for now.
master <- subset(master, select = -c(25))
master <- master[,-c(1:2)]
View(master)
```

Getting the Neighboring Border File

```{r}
AllT21ContigencyRatios <- rio::import("../../Data/borderratios.csv")
AllT21ContigencyRatios <- AllT21ContigencyRatios[-1]
AllT21ContigencyRatios$ratio <- as.numeric(AllT21ContigencyRatios$ratio)
```

Joining the two files for Analysis
```{r}
nrow(master)
nrow(AllT21ContigencyRatios)
#names(AllT21ContingencyRatios)

master$Name.x <- tolower(master$Name.x)
#master$Name.x
#match(unique(master$Name.x), unique(AllT21ContingencyRatios$TownName))
#match(unique(master$Year), unique(AllT21ContingencyRatios$year))

T21_Contigency_Master <- master %>% left_join(AllT21ContigencyRatios, by = c("Name.x" = "TownName", "Year" = "year")) 
#View(T21_Contingency_Master)
```

Cleaning the combined data set further for analysis
```{r}
T21_Contigency_Master <- T21_Contigency_Master[T21_Contigency_Master$Event !=2,]
T21_Contigency_Master$Population <- as.numeric(T21_Contigency_Master$Population)
#sort(names(T21_Contingency_Master))
#T21_Contingency_Master$ratio
T21_Contigency_Master$ratio <- as.numeric(T21_Contigency_Master$ratio)
```

Unconditional Mean Models for Random Effect Lowest Level

?Function to test UMM to the lowest level Random Effects Test
```{r}
glmer.fit1 <- glmer(Event ~ (1|Year), family = binomial, data = T21_Contigency_Master)
#rand(glmer.fit1) #What is there to use?
```




Check if we need random effects of Counties?
It is statistically significant to include the County Level Random Effects
```{r}
glmer.fit2 <- glmer(Event ~ (1|Year/County), family = binomial, data = T21_Contigency_Master)
```

Checking if the Year Random Effect is needed
```{r}
anova(glmer.fit1, glmer.fit2)
```

ICC Interpretations

Where are the residuals?
```{r}
print(summary(glmer.fit1))
```

```{r}
print(summary(glmer.fit2))
```





